APPM report - Draft

### 2022-11-11 paper_version/main.tex
fix some English syntax mistakes

To obtain the semi-discretization, we first integrate (\ref{equ:euler_conservation}) over a cell $V_i$ 
\begin{equation} \label{equ:euler_grid} 
    \dot{\overline{\mathbf{U}}}_i + \frac{1}{|V_i|}\sum_{j:A_j\in\partial V_i} |A_j|\underbrace{\frac{1}{|A_j|}\iint_{A_j}\mathbf{f}(\mathbf{U})\cdot \mathbf{n}_j \text{d}A}_{:= \overline{\mathbf{f}}_j \approx \mathbf{f}^\text{num}_j} = \underbrace{\frac{1}{|V_i|}\iiint_{V_i} \mathbf{RHS} \text{d}V}_{:= \overline{\mathbf{RHS}}_i}
\end{equation}
where $\overline{\mathbf{U}}_i := \iiint_{V_i} \mathbf{U} \text{d}V / |V_i| \in L^2([0,T],\mathbb{R}^m)$ is the cell average of $\mathbf{U}$ and $\mathbf{n}_j$ is the outer normal vector of face $A_j$ with respect to the cell $V_i$. We approximate the flux $\overline{\mathbf{f}}_j$ in (\ref{equ:euler_grid}) by a numerical flux $\mathbf{f}^\text{num}_j := \mathbf{f}^\text{num}\left(\overline{\mathbf{U}}_i, \overline{\mathbf{U}}_{k(i,j)}, \mathbf{n}_j\right)$, where $k(i,j)$ returns the index of the adjacent cell that shares $A_j$ with cell $V_i$. Classical numerical fluxes include Lax-Friedrich flux, Rusanov flux, Engquist-Osher flux, see \cite[][p. 44-46]{mishra_2019}. Finally, we end up with the semi-discretized equation:
\begin{equation}
    \dot{\overline{\mathbf{U}}}_i + \frac{1}{|V_i|}\sum_{j:A_j\in\partial V_i} |A_j| \mathbf{f}^\text{num}\left(\overline{\mathbf{U}}_i, \overline{\mathbf{U}}_{k(i,j)}, \mathbf{n}_j\right) = \overline{\mathbf{RHS}}_i.
    \label{equ:fvm}
\end{equation}
The Rusanov flux in multi-dimensions on face $A_j$ writes
\begin{equation} \label{equ:rusanov-flux-3d}
    \mathbf{f}^\text{num}\left(\overline{\mathbf{U}}_L, \overline{\mathbf{U}}_R, \mathbf{n}\right) = \frac{1}{2}\left[\mathbf{f}(\overline{\mathbf{U}}_L)\cdot\mathbf{n} + \mathbf{f}(\overline{\mathbf{U}}_R)\cdot\mathbf{n}\right] - \frac{1}{2}\overline{s}\left(\overline{\mathbf{U}}_R - \overline{\mathbf{U}}_L\right),  
\end{equation}
where $\overline{s} = \text{max}(s(\overline{\mathbf{U}}_L), s(\overline{\mathbf{U}}_R))$ with $s(\mathbf{U}) := |\mathbf{u}\cdot\mathbf{n}| + \sqrt{\gamma p/\rho}$ representing the largest wave speed.

We would like to emphasis that the Euler system is discretized on $\mathcal{M}'$ due to the fact that 1) the electric current is connected to the momenta of charged particles by (\ref{equ:maxwell_euler_coupling}); 2) the electric current is discretized on dual faces by (\ref{equ:maxwell_grid_ampere}).

@@

The problem is twofold:
\begin{itemize}
    \item[-] given the fluxes at faces of a cell, reconstruct the vector field inside the cell;
    \item[-] given the integrals along edges of a cell, reconstruct the vector field inside the cell. 
\end{itemize}
We adopt the principle of least square fitting, and reconstruct a \emph{constant} vector field inside each cell. For a cell $\Tilde{V}$ with $k$ faces with areas $\{A_i\}_{i=1}^k$, normal vectors $\{\mathbf{n}_i\}_{i=1}^k$ and fluxes $\{f_i\}_{i=1}^k$, a constant vector field $\mathbf{v}$ satisfying 
\begin{equation*}
    \mathbf{v} = \argmin_{v\in \mathbb{R}^3} \sum_{i=1}^k(A_i\mathbf{v} \cdot \mathbf{n}_i - f_i)^2.   
\end{equation*} can be computed through
\begin{equation*}
    \mathbf{v} = (\mathbb{K}^T\mathbb{K})^{-1}\mathbb{K}^T\mathbf{f},
\end{equation*}
where
\begin{equation*}
    \mathbb{K} = [A_1\mathbf{n}_1, A_2\mathbf{n}_2, \cdots, A_k\mathbf{n}_k]^T,\ \ \ \mathbf{f} = [f_1, f_2, \cdots, f_k]^T,
\end{equation*}
and each vector in $\mathbb{R}^3$ is treated as a column vector. The construction based on the integral quantities on edges can be done similarly. Assembling the local constructions for each dual cell, the global construction can be written as 
\begin{equation}
    \mathbf{E} = \Tilde{\mathbb{R}}_E\mathbf{d},
    \ \ \ \ 
    \mathbf{B} = \Tilde{\mathbb{R}}_B\mathbf{b}, \label{equ:reconstruction}
\end{equation}
where $\mathbf{d}, \mathbf{b}$ are stacked unknowns, see Tab. \ref{tab:def_size_var}; $\mathbf{E} := (\mathbf{E}_i)_{i=1}^{N_{\Tilde{V}}}$ and $\mathbf{B} := (\mathbf{B}_i)_{i=1}^{N_{\Tilde{V}}}$ are $N_{\Tilde{V}} \times 3$ matrices stacking the reconstructed $\mathbf{E}$-fields and $\mathbf{B}$-fields at each $\Tilde{V}$; $\Tilde{\mathbb{R}}_E$ and $\Tilde{\mathbb{R}}_B$ are thus rank-3 tensors.

@@

\subsubsection{Discrete Boundary Conditions}
The BCs for the Euler system (see Section \ref{sec:BC}) are implemented by the approach of ghost cells \cite[][ch. 7]{leveque_2007}, i.e. thinking of extending the domain by a few additional cells and prescribing the variables. In our case, the ghost cells at the open boundary at $\Gamma_C$ are set to have the equal values as the interior ones that are adjacent. It is equivalent to enforce the numerical fluxes
\begin{equation*}
    \mathbf{F}_i = {\mathbf{f}^\text{num}}(\mathbf{U}_j, \mathbf{U}_j, \mathbf{n}_i), \ \ \forall i: \Tilde{A}_i \subset \Gamma_C,
\end{equation*}
where $j$ refers to the index of the cell adjacent to the boundary face $\Tilde{A}_i$ and is unique. For the reflective wall $\Gamma_W$, the momentum of a ghost cell are reversed with respect to its adjacent one while keeping the other quantities unchanged. Therefore, the numerical fluxes are 
\begin{equation*}
    \mathbf{F}_i = \mathbf{f}^\text{num}(\mathbf{U}_j, \hat{\mathbf{U}}_j, \mathbf{n}_i), \ \ \forall i: \Tilde{A}_i \subset \Gamma_W,
\end{equation*}
where the value of the ghost cell $\hat{\mathbf{U}} = [n, n\mathbf{u} - 2(\mathbf{n}\cdot\mathbf{u})\mathbf{n}, ne]^T$ reverses the normal velocity of $\mathbf{U} = [n, n\mathbf{u}, ne]^T$.

>>>>

To obtain the semi-discretization, we first integrate (\ref{equ:euler_conservation}) over a cell $V_i$ 
\begin{equation} \label{equ:euler_grid} 
    \dot{\overline{\mathbf{U}}}_i + \frac{1}{|V_i|}\sum_{j:A_j\in\partial V_i} |A_j|\underbrace{\frac{1}{|A_j|}\iint_{A_j}\mathbf{f}(\mathbf{U})\cdot \mathbf{n}_j \text{d}A}_{:= \overline{\mathbf{f}}_j \approx \mathbf{f}^\text{num}_j} = \underbrace{\frac{1}{|V_i|}\iiint_{V_i} \mathbf{RHS} \text{d}V}_{:= \overline{\mathbf{RHS}}_i}
\end{equation}
where $\overline{\mathbf{U}}_i := \iiint_{V_i} \mathbf{U} \text{d}V / |V_i| \in L^2([0,T],\mathbb{R}^m)$ is the cell average of $\mathbf{U}$ and $\mathbf{n}_j$ is the outer normal vector of face $A_j$ with respect to the cell $V_i$. We approximate the flux $\overline{\mathbf{f}}_j$ in (\ref{equ:euler_grid}) by a numerical flux $\mathbf{f}^\text{num}_j := \mathbf{f}^\text{num}\left(\overline{\mathbf{U}}_i, \overline{\mathbf{U}}_{k(i,j)}, \mathbf{n}_j\right)$, where $k(i,j)$ returns the index of the adjacent cell that shares $A_j$ with cell $V_i$. Classical numerical fluxes include Lax-Friedrich flux, Rusanov flux, and Engquist-Osher flux, see \cite[][p. 44-46]{mishra_2019}. Finally, we end up with the semi-discretized equation:
\begin{equation}
    \dot{\overline{\mathbf{U}}}_i + \frac{1}{|V_i|}\sum_{j:A_j\in\partial V_i} |A_j| \mathbf{f}^\text{num}\left(\overline{\mathbf{U}}_i, \overline{\mathbf{U}}_{k(i,j)}, \mathbf{n}_j\right) = \overline{\mathbf{RHS}}_i.
    \label{equ:fvm}
\end{equation}
The Rusanov flux in multi-dimensions on face $A_j$ writes
\begin{equation} \label{equ:rusanov-flux-3d}
    \mathbf{f}^\text{num}\left(\overline{\mathbf{U}}_L, \overline{\mathbf{U}}_R, \mathbf{n}\right) = \frac{1}{2}\left[\mathbf{f}(\overline{\mathbf{U}}_L)\cdot\mathbf{n} + \mathbf{f}(\overline{\mathbf{U}}_R)\cdot\mathbf{n}\right] - \frac{1}{2}\overline{s}\left(\overline{\mathbf{U}}_R - \overline{\mathbf{U}}_L\right),  
\end{equation}
where $\overline{s} = \text{max}(s(\overline{\mathbf{U}}_L), s(\overline{\mathbf{U}}_R))$ with $s(\mathbf{U}) := |\mathbf{u}\cdot\mathbf{n}| + \sqrt{\gamma p/\rho}$ representing the largest wave speed.

We would like to emphasize that the Euler system is discretized on $\mathcal{M}'$ due to the fact that 1) the electric current is connected to the momenta of charged particles by (\ref{equ:maxwell_euler_coupling}); 2) the electric current is discretized on dual faces by (\ref{equ:maxwell_grid_ampere}).

@@

The problem is twofold:
\begin{itemize}
    \item[-] given the fluxes at faces of a cell, reconstruct the vector field inside the cell;
    \item[-] given the integrals along the edges of a cell, reconstruct the vector field inside the cell. 
\end{itemize}
We adopt the principle of least square fitting and reconstruct a \emph{constant} vector field inside each cell. For a cell $\Tilde{V}$ with $k$ faces with areas $\{A_i\}_{i=1}^k$, normal vectors $\{\mathbf{n}_i\}_{i=1}^k$ and fluxes $\{f_i\}_{i=1}^k$, a constant vector field $\mathbf{v}$ satisfying 
\begin{equation*}
    \mathbf{v} = \argmin_{v\in \mathbb{R}^3} \sum_{i=1}^k(A_i\mathbf{v} \cdot \mathbf{n}_i - f_i)^2.   
\end{equation*} can be computed through
\begin{equation*}
    \mathbf{v} = (\mathbb{K}^T\mathbb{K})^{-1}\mathbb{K}^T\mathbf{f},
\end{equation*}
where
\begin{equation*}
    \mathbb{K} = [A_1\mathbf{n}_1, A_2\mathbf{n}_2, \cdots, A_k\mathbf{n}_k]^T,\ \ \ \mathbf{f} = [f_1, f_2, \cdots, f_k]^T,
\end{equation*}
and each vector in $\mathbb{R}^3$ is treated as a column vector. The construction based on the integral quantities on edges can be done similarly. Assembling the local constructions for each dual cell, the global construction can be written as 
\begin{equation}
    \mathbf{E} = \Tilde{\mathbb{R}}_E\mathbf{d},
    \ \ \ \ 
    \mathbf{B} = \Tilde{\mathbb{R}}_B\mathbf{b}, \label{equ:reconstruction}
\end{equation}
where $\mathbf{d}, \mathbf{b}$ are stacked unknowns, see Tab. \ref{tab:def_size_var}; $\mathbf{E} := (\mathbf{E}_i)_{i=1}^{N_{\Tilde{V}}}$ and $\mathbf{B} := (\mathbf{B}_i)_{i=1}^{N_{\Tilde{V}}}$ are $N_{\Tilde{V}} \times 3$ matrices stacking the reconstructed $\mathbf{E}$-fields and $\mathbf{B}$-fields at each $\Tilde{V}$; $\Tilde{\mathbb{R}}_E$ and $\Tilde{\mathbb{R}}_B$ are thus rank-3 tensors.

@@

\subsubsection{Discrete Boundary Conditions}
The BCs for the Euler system (see Section \ref{sec:BC}) are implemented by the approach of ghost cells \cite[][ch. 7]{leveque_2007}, i.e. thinking of extending the domain by a few additional cells and prescribing the variables. In our case, the ghost cells at the open boundary at $\Gamma_C$ are set to have equal values as the interior ones that are adjacent. It is equivalent to enforcing the numerical fluxes
\begin{equation*}
    \mathbf{F}_i = {\mathbf{f}^\text{num}}(\mathbf{U}_j, \mathbf{U}_j, \mathbf{n}_i), \ \ \forall i: \Tilde{A}_i \subset \Gamma_C,
\end{equation*}
where $j$ refers to the index of the cell adjacent to the boundary face $\Tilde{A}_i$ and is unique. For the reflective wall $\Gamma_W$, the momentum of a ghost cell is reversed with respect to its adjacent one while keeping the other quantities unchanged. Therefore, the numerical fluxes are 
\begin{equation*}
    \mathbf{F}_i = \mathbf{f}^\text{num}(\mathbf{U}_j, \hat{\mathbf{U}}_j, \mathbf{n}_i), \ \ \forall i: \Tilde{A}_i \subset \Gamma_W,
\end{equation*}
where the value of the ghost cell $\hat{\mathbf{U}} = [n, n\mathbf{u} - 2(\mathbf{n}\cdot\mathbf{u})\mathbf{n}, ne]^T$ reverses the normal velocity of $\mathbf{U} = [n, n\mathbf{u}, ne]^T$.
